On the application of microwave-acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-05-25 documents/paper.tex
LO test something more

\usepackage[left=2cm,right=2cm,
			top=2.25cm,
			bottom=2.25cm,%
			headheight=11pt,%
			letterpaper]{geometry}

\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{blindtext,graphicx}
\usepackage[absolute]{textpos}
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}

\title{The Triangulation of Titling Data in Non-Linear Gaussian Fashion via $\rho$ Series\thanks{No procrastination}}
\date{2017\\ December}
\author{John Doe\\ Magic Department\thanks{I am no longer a member of this department}, Richard Miles University 
\and Richard Row, \LaTeX\ Academy}

@@

This work was prepared by an undergraduate and has not been peer-reviewed. 
Please consider all claims with the appropriate skepticism.

\begin{textblock}{5}(14,1)
\noindent University of Nowhere
\end{textblock}
\begin{textblock}{5}(1,27)
\end{textblock}

\null\hfill\begin{tabular}[t]{l@{}}
  \textbf{My e} \\
  \textit{My University}
\end{tabular}

\begin{abstract}
We extend this landmark work rather trivially by:
\begin{itemize}
  \item Testing the time dependence of inactivation
  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can be produced in 10 million-of quantities using existing PCB infrastructure  
  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
  \item Discussing the biological basis for the safety of the device
  \item Showing that the deviation from the expected theshold could be explained by variance in the 
\end{itemize}
\end{abstract}

@@

@@

The following properties: P1dB

For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.

\paragraph{} Feedback-loop-oscillator

@@

@@

 gate must be weakly biased to ground, otherwise stray charge destroys the oscillation.

@@

If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm at these frequencies) terminated with a stub to produce a virtual short or open circuit [Seo 2007].

However, reflections from these structures still appeared to distort signals beyond repair, even with wideband half-moon stubs [Syrett 1980].

\noindent\fbox{\parbox{\linewidth}{
	Rebuke: despite this blather, many other papers have had success with VCOs at these frequencies.

}}

In production, these could be accomodated by graphite-polymer resistors.

Timeline

>>>>

\usepackage[left=2cm,right=2cm,
			top=1.25cm,
			bottom=2.25cm,%
			headheight=11pt,%
			letterpaper]{geometry}

\frenchspacing

\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{blindtext,graphicx}
\usepackage[absolute]{textpos}
\usepackage[parfill]{parskip}
\usepackage[colorlinks]{hyperref}

\usepackage{tcolorbox}
\newtcolorbox{autem}{colback=red!5!white,colframe=red!75!black}
\newtcolorbox{toolchain}{colback=blue!5!white,colframe=blue!40!black!40}
%https://tex.stackexchange.com/questions/66154/how-to-construct-a-coloured-box-with-rounded-corners

%\usepackage[sfdefault,light]{roboto}

\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}

\title{On the application of microwave-acoustic resonant viral inactivation
\thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
\date{May 2020}
\author{Based primarily on exceptional work by }

@@

This work was prepared by an undergraduate and has not been peer-reviewed.

Additionally, the author has no prior experience with either biology or microwave design.

Testing was only performed with a surrogate bacteriophage. All experiments must be repeated with Inf. A and then SARS-NCoV-2.

Please consider all claims with appropriate skepticism.

\begin{textblock}{5}(1,1)
\noindent Please view the latest version at github.com/0xDBFB7/covidinator
\end{textblock}
%\begin{textblock}{5}(1,27)
%\end{textblock}

\null\begin{tabular}[t]{l@{}}
  {Daniel Correia} \\
  \textit{York University}
\end{tabular}

\begin{abstract}

Brief:

Aims:
We extend this landmark work rather trivially by:
\begin{itemize}
  \item Establishing the time dependence of inactivation
  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
  \item Discussing the biological basis for the safety of the device
  \item Showing that the deviation from the expected theshold could be explained by variance in the 
\end{itemize}
\end{abstract}

@@

\begin{toolchain}
	{\it \bf [Yang 2015]'s toolchain}
	\begin{itemize}
	\item Envelope/liposome breaking strength and stiffness from AFM nanoindentation data
	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
	\item Experimental data from microwave cuvette to 
	\item COMSOL finite-element for illustration
	\end{itemize}
\end{toolchain}

\paragraph{\textbf{Time dependence}}\

Both Yang and [] used an apparently arbitrary 15-minute exposure in their tests - a very reasonable decision given the focus of their paper.

To determine the effectiveness against airborne particles, and to minimize the power required in a dwelling phased-array beam, we must first establish the required duration of exposure.

{\color{red} speculative hypothesizing \{ }

In contrast to chemical inactivation, where the time dependence appears to be dominated by viscous fluid dynamic effects [Hirose 2017], or UV inactivation, where a certain dose of photons must be absorbed, one might expect RF

As a damped, driven oscillator, the ring-up time of the virus depends on the Q factor. Yang et al. state the Q of Inf. A as between 2 and 10, so at 8 GHz the steady-state amplitude should be reached in well under 1 us.

[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture. Such a mechanism could perhaps extend the exposure required to break the capsid or membrane. Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the lipid fractures,

{\color{red}  \} }

@@

\noindent\fbox{\parbox{\linewidth}{
	Toolchain:
	\begin{itemize}
	\item QUCS 0.0.20 for AC simulation, with python-qucs and scipy's 'basinhopper' for optimization
	\item gprMax for FDTD EM simulation
	\item KiCAD, wcalc, scikit-rf
	\end{itemize}
}}
%
The following properties: P1dB

For ease of design and simulation, a device with Touchstone S-parameters and SPICE files is greatly preferable.
%
\paragraph{\textbf{The feedback loop oscillator}}\

Oscillators must meet the Barkhausen criterion:

\begin{itemize}

\item A 360 degree phase shift around the feedback loop (including the phase shift contribution from the amplifier, which itself varies greatly with frequency)
\item A loop gain $>1.$

\end{itemize}\
%
Generally a third element is also used:
%
\begin{itemize}
\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
\end{itemize}
%
We encountered proximity effects from reflections and near-field coupling off nearby flesh; if this instablity, mode-hopping and de-tuning becomes an issue, it could be mitigated by way of shielding (adding a manufacturing step), or a tight filter around the desired mode.

 design of a triple-tuned oscillator.

@@

\paragraph{Biasing}\

@@

The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.

@@

If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].

However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].

\noindent\fbox{\parbox{\linewidth}{
	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
}}

In production, these could be accomodated by graphite-polymer printed resistors.

Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.

%\noindent\fbox{\parbox{\linewidth}{
\begin{autem}
	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
\end{autem}

[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.

The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).

{\Large Mass production}

{\Large Captain's Log, Supplemental}

\paragraph{Timeline}

\paragraph{Comments by others}

\paragraph{Lessons Learned}

When iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test. Including a picture with a webcam of the assembled board is also helpful.

Version control alone isn't quite enough. Just having a simulation setup file somewhere in the commit history isn't "discoverable" - that is, you should be able to see what the input and output was without re-running the simulation; and manually taking notes tended to disrupt the flow of testing.

Write a paper to be understood; to be as clear and helpful as possible to the reader.
